---
title: "Example R Markdown 1"
author: "carina"
date: "09/12/2020"
output:
  html_document:
    theme: cosmo
    highlight: tango
    toc: true
    toc_depht: 3
    number_sections: true
    toc_float:
      collapsed: no 
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '3'
---





## Prepare for analyses

```{r }
library(lattice)
```


## Basic console output
To insert an R code chunk, you can type it manually or just press `Chunks - Insert chunks` or use the shortcut key. This will produce the following code chunk:

    ```{r  }
    
    ```

Pressing tab when inside the braces will bring up code chunk options.

The following R code chunk labelled `basicconsole` is as follows:

    ```{r }
    x <- 1:10
    y <- round(rnorm(10, x, 1), 2)
    df <- data.frame(x, y)
    df
    ```
    
The code chunk input and output is then displayed as follows:

```{r basicconsole}
x <- 1:10
y <- round(rnorm(10, x, 1), 2)
df <- data.frame(x, y)
df
```

## Plots
Images generated by `knitr` are saved in a figures folder and also are embebed in the HTML document.

### Simple plot
Here is a basic plot using base graphics:

    ```{r }
    plot(x)
    ```

```{r simpleplot}
plot(x)
```

Note that unlike traditional Sweave, there is no need to write `fig=TRUE`.


### Multiple plots
Also you can include multiple plots in one code chunk:

    ```{r }
    boxplot(1:10~rep(1:2,5))
    plot(x, y)
    ```

```{r multipleplots}
boxplot(1:10~rep(1:2,5))
plot(x, y)
```


### `lattice` plot
As do lattice plots:

```{r latticeex}
library(lattice)
xyplot(y~x)
```



## R Code chunk features
### Create Markdown code from R


The following code hides the command input (i.e., `echo=FALSE`), and outputs the content directly as code.

    ```{r , results='asis', echo=FALSE}
    cat("Here are some dot points\n\n")
    cat(paste("* The value of y[", 1:3, "] is ", y[1:3], sep="", collapse="\n"))
    ```



### Control figure size
The following is an example of a smaller figure using `fig.width` and `fig.height` options.

    ```{r , fig.width=3, fig.height=3}
    plot(x)
    ```

```{r bigplot, fig.width=8, fig.height=8}
plot(x)
```



## Basic markdown functionality

### Dot Points
Simple dot points:

* Point 1
* Point 2
* Point 3

and numeric dot points:

1. Number 1
2. Number 2
3. Number 3

and nested dot points:

* A
    * A.1
    * A.2
* B
    * B.1
    * B.2


### Equations
Equations are included by using LaTeX notation and including them either between single dollar signs (inline equations) or double dollar signs (displayed equations).


There are inline equations such as $y_i = \alpha + \beta x_i + e_i$.

And displayed formulas:

$$\frac{1}{1+\exp(-x)}$$




### Tables
Tables can be included using the following notation

A  | B | C
--- | --- | ---
1  | Male | Blue
2  | Female | Pink




### Code
Here is Markdown R code chunk displayed as code:

    ```{r}
    x <- 1:10
    x
    ```
    


And then there's inline code such as `x <- 1:10`.

### Quote
Let's quote some stuff:

> To be, or not to be, that is the question
